The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$

### 2016-01-12 submission3r1.tex
Fix complete intersection statements

Consider the ideal $I_c = \langle f_1, \ldots, f_{n - 1} \rangle \subset A$ generated by the $f_i$.  In this section, we will show that $A/I_c$ is a complete intersection, for which we require some preparatory computations.

In the general case of an ideal $I$ in a polynomial ring $k[X_1,\dots,X_n]$, $k[X_1,\dots,X_m]/I$ is a complete intersection if $I$ is generated by $l$ elements with $\dim k[X_1,\dots,X_n]/I=m-l$.

@@

\begin{proposition}\label{prop:ci}
For generic $c$, the quotient $A/I_c$ is a complete intersection. 
\end{proposition}
\begin{proof}
By Proposition~\ref{prop:linind}, $I_c$ has $n-1$ linearly independent generators $\{f_i\}$. Hence we wish to show that $A/I_c$ has dimension $0$, for which it suffices to show that if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for all $i$, then $\alpha_1=\dots=\alpha_{n}=0$.

>>>>

Consider the ideal $I_c = \langle f_1, \ldots, f_{n - 1} \rangle \subset A$ generated by the $f_i$.  In this section, we will show that $A/I_c$ is a complete intersection.  Recall that for an ideal $I \subset k[X_1,\dots,X_m]$, the quotient ring $k[X_1,\dots,X_m]/I$ is a complete intersection if $I$ has a minimal set of generators $g_1, \ldots, g_l$ with $\dim k[X_1,\dots,X_m]/I = m - l$. We require now some preparatory computations.

@@

\begin{proposition}\label{prop:ci}
For generic $c$, the quotient $A/I_c$ is a complete intersection. 
\end{proposition}
\begin{proof}
By Proposition~\ref{prop:linind}, $I_c$ has a set of $n-1$ linearly independent and therefore minimal generators $\{f_i\}$ in degree $p$.  We will now show that if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for all $i$, then $\alpha_1=\dots=\alpha_{n}=0$.  This will imply that $\supp A/I_c = \{(0, \ldots, 0)\}$ and hence $A/I_c$ has dimension $0$, completing the proof.
